---
title: "Methodology"
description: |
  This webpage describes the methodology deployed in the crime investigation journey.
author:
  - name: Vertika Poddar
    affiliation: Singapore Management University
date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(fig.retina =3,
                      echo = TRUE,
                      eval = TRUE,
                      message = FALSE,
                      warning = FALSE)
```

The code chunk below is used to load and install all the necessary packages

```{r}
packages = c('readr','ggiraph','igraph', 'tidyverse','plotly','lubridate','raster', 'sf', 'tmap','DT', 'greekLetters', 'clock', 'crosstalk')
for (p in packages){
  if(!require(p, character.only = T)){
    install.packages(p)
  }
  library(p, character.only = T)
}
```

The code chunk below imports the data

```{r}
cc_data <- read_csv("C:/vertikapoddar/Assignment/data/cc_data.csv")
lc_data <- read_csv("C:/vertikapoddar/Assignment/data/loyalty_data.csv")
gps_data <- read_csv("C:/vertikapoddar/Assignment/data/gps.csv")
emp_data <- read_csv("C:/vertikapoddar/Assignment/data/car-assignments.csv")
```

We will examine the structure of the imported dataframe using *glimpse()* of **dplyr**

```{r}
glimpse(cc_data)
glimpse(lc_data)
glimpse(gps_data)
glimpse(emp_data)
```

**Comments / Observations** : *timestamp* of *cc_data*, *lc_data* and *gps_data* is 'Character' data type instead of 'Date' type. Modify the data type to 'Date' before proceeding. Also, *last4ccnum* of *cc_data*, *id* of *gps_data* and *CarID* of *emp_data* needs to be transformed to 'Character' type.

**Wrangling Data Set**

The code chunk below will perform the required changes

```{r}
cc_data$timestamp = mdy_hm(cc_data$timestamp)
cc_data$day = get_day(cc_data$timestamp)
cc_data$hour = get_hour(cc_data$timestamp)
lc_data$timestamp = mdy(lc_data$timestamp)
lc_data$loyaltynum = as_factor(lc_data$loyaltynum)
gps_data$Timestamp = mdy_hms(gps_data$Timestamp)
gps_data$id = as_factor(gps_data$id)
emp_data$CarID = as_factor(emp_data$CarID)
gps_data$day =  get_day(gps_data$Timestamp)
gps_data$hour = get_hour(gps_data$Timestamp)
```

Start analysing the dataset by counting the number of cards in both the dataframes.

The code chuck below counts the number of unique cards in the credit card dataset.

```{r}
cc_count <- unique(cc_data$last4ccnum)
length(cc_count)
```
The code chuck below counts the number of unique cards in the loyalty card dataset.

```{r}
lc_count <- unique(lc_data$loyaltynum)
length(lc_count)
```

To find out the most popular location using the credit card and loyalty card data, combine the two dataset, below is the code chunk:

```{r}
cc_freq <- cc_data %>%
  count(location) %>%
  rename(credit_card = n)

lc_freq <- lc_data %>%
  count(location) %>%
  rename(loyalty_card = n)

cc_lc_freq <- full_join(cc_freq, lc_freq, by = "location" )
```

```{r}
xform <- list(categoryorder ="total ascending",
              categoryarray = c((cc_lc_freq$location)),
              tickfont = list(size =6))


popular_location <- plot_ly(cc_lc_freq, x = ~credit_card, y = ~location, type = 'bar', name = 'credit_card', text = ~credit_card, textposition = 'auto')
popular_location <- popular_location %>%
  add_trace(x = ~loyalty_card, name = 'loyalty_card', text = ~loyalty_card, textposition = 'auto')
popular_location <- popular_location %>%
  layout(title = "Frequency chart for locations as per credit card and loyalyty card data", 
         xaxis = list(title = 'number of vists'), 
         barmode = 'group', 
         yaxis = xform)

popular_location
```

```{r}
cc_filter <- cc_data %>%
  filter(day == 6, hour == 7)

cc_filter %>%
  group_by(location) %>%
  summarize(n_vists = n())
```

```{r}
cc_time <- cc_data %>%
  group_by(hour, location) %>%
  summarize(n_vists = n())

cc_time
```

Below is the code chunk to work with geospatial data

QGIS software has been used to georeference the map with the coordinates.

```{r}
bgmap <- raster("C:/vertikapoddar/data/MC2.tif")
bgmap
```

```{r}
tm_shape(bgmap) + 
  tm_rgb(bgmap, r = 1, g = 2, b = 3,
         alpha = NA,
         saturation = 1,
         interpolate = TRUE,
         max.value = 255)
```

```{r}
Abila_st <- st_read(dsn = "C:/vertikapoddar/Assignment/data/Geospatial",
                    layer = "Abila")
```

```{r}
gps_sf <- st_as_sf(gps_data, 
                   coords = c("long", "lat"),
                   crs = 4326)
```

```{r}
gps_path <- gps_sf %>%
  group_by(day, hour) %>%
  summarize(m = mean(Timestamp),
            do_union = FALSE) %>%
  st_cast("LINESTRING")
```

```{r}
gps_path_selected <- gps_path %>%
  filter(day == 6, hour == 10)
tmap_mode("view")
tm_shape(bgmap) +
tm_rgb(bgmap, r = 1, g = 2, b = 3,
         alpha = NA,
         saturation = 1,
         interpolate = TRUE,
         max.value = 255) +
  tm_shape(gps_path_selected) +
  tm_lines()
```
